The Dynamics of Normalization Reweighting

### 2022-05-17 manuscript.Rmd
Included MEG analysis code

MEGmeantime5HzCON <- matrix(0,nrow=4,ncol=8009) 
MEGmeantime7HzCON <- matrix(0,nrow=4,ncol=8009) 
MEGmeantime5HzASD <- matrix(0,nrow=4,ncol=8009) 
MEGmeantime7HzASD <- matrix(0,nrow=4,ncol=8009) 
for (cond in 1:4){
MEGmeantime7HzCON[cond,] <- apply(abs(MEGtimecourse7Hz[which(sortedgroups==1),cond,]),2,mean)
MEGmeantime5HzCON[cond,] <- apply(abs(MEGtimecourse5Hz[which(sortedgroups==1),cond,]),2,mean)
MEGmeantime7HzASD[cond,] <- apply(abs(MEGtimecourse7Hz[which(sortedgroups==2),cond,]),2,mean)
MEGmeantime5HzASD[cond,] <- apply(abs(MEGtimecourse5Hz[which(sortedgroups==2),cond,]),2,mean)
}

@@

# lines(times,1000*MEGmeantime5Hz[1,],lwd=2,col='red')
# lines(times,1000*MEGmeantime5Hz[2,],lwd=2,col='green')
# lines(times,1000*MEGmeantime5Hz[3,],lwd=2,col='blue')
# lines(times,1000*MEGmeantime5Hz[4,],lwd=2,col='orange')
spl5a <- smooth.spline(times,1000*MEGmeantime5Hz[1,],df=20)
lines(spl5a$x,spl5a$y,col='red',lwd=2)
spl5b <- smooth.spline(times,1000*MEGmeantime5Hz[2,],df=20)
lines(spl5b$x,spl5b$y,col='green',lwd=2)
spl5c <- smooth.spline(times,1000*MEGmeantime5Hz[3,],df=20)
lines(spl5c$x,spl5c$y,col='blue',lwd=2)
spl5d <- smooth.spline(times,1000*MEGmeantime5Hz[4,],df=20)
lines(spl5d$x,spl5d$y,col='orange',lwd=2)

# lines(times,1000*MEGmeantime5HzASD[1,],lwd=2,col='red',lty=2)
# lines(times,1000*MEGmeantime5HzASD[2,],lwd=2,col='green',lty=2)
# lines(times,1000*MEGmeantime5HzASD[3,],lwd=2,col='blue',lty=2)
# lines(times,1000*MEGmeantime5HzASD[4,],lwd=2,col='orange',lty=2)
spl5aASD <- smooth.spline(times,1000*MEGmeantime5HzASD[1,],df=20)
lines(spl5aASD$x,spl5aASD$y,col='red',lwd=2,lty=2)
spl5bASD <- smooth.spline(times,1000*MEGmeantime5HzASD[2,],df=20)
lines(spl5bASD$x,spl5bASD$y,col='green',lwd=2,lty=2)
spl5cASD <- smooth.spline(times,1000*MEGmeantime5HzASD[3,],df=20)
lines(spl5cASD$x,spl5cASD$y,col='blue',lwd=2,lty=2)
spl5dASD <- smooth.spline(times,1000*MEGmeantime5HzASD[4,],df=20)
lines(spl5dASD$x,spl5dASD$y,col='orange',lwd=2,lty=2)

# lines(times,1000*MEGmeantime5HzCON[1,],lwd=2,col='red',lty=3)
# lines(times,1000*MEGmeantime5HzCON[2,],lwd=2,col='green',lty=3)
# lines(times,1000*MEGmeantime5HzCON[3,],lwd=2,col='blue',lty=3)
# lines(times,1000*MEGmeantime5HzCON[4,],lwd=2,col='orange',lty=3)
spl5aCON <- smooth.spline(times,1000*MEGmeantime5HzCON[1,],df=20)
lines(spl5aCON$x,spl5aCON$y,col='red',lwd=2,lty=3)
spl5bCON <- smooth.spline(times,1000*MEGmeantime5HzCON[2,],df=20)
lines(spl5bCON$x,spl5bCON$y,col='green',lwd=2,lty=3)
spl5cCON <- smooth.spline(times,1000*MEGmeantime5HzCON[3,],df=20)
lines(spl5cCON$x,spl5cCON$y,col='blue',lwd=2,lty=3)
spl5dCON <- smooth.spline(times,1000*MEGmeantime5HzCON[4,],df=20)
lines(spl5dCON$x,spl5dCON$y,col='orange',lwd=2,lty=3)

@@

lines(spl5bASD$x,spl5aASD$y/spl5cASD$y,col='blue',lwd=2,lty=2)
lines(spl5bASD$x,spl5aASD$y/spl5dASD$y,col='orange',lwd=2,lty=2)

lines(spl5bCON$x,spl5aCON$y/spl5cCON$y,col='blue',lwd=2,lty=3)
lines(spl5bCON$x,spl5aCON$y/spl5dCON$y,col='orange',lwd=2,lty=3)

@@

# lines(times,1000*MEGmeantime7Hz[1,],lwd=2,col='red')
# lines(times,1000*MEGmeantime7Hz[2,],lwd=2,col='green')
# lines(times,1000*MEGmeantime7Hz[3,],lwd=2,col='blue')
# lines(times,1000*MEGmeantime7Hz[4,],lwd=2,col='orange')
spl7a <- smooth.spline(times,1000*MEGmeantime7Hz[1,],df=20)
lines(spl7a$x,spl7a$y,col='red',lwd=2)
spl7b <- smooth.spline(times,1000*MEGmeantime7Hz[2,],df=20)
lines(spl7b$x,spl7b$y,col='green',lwd=2)
spl7c <- smooth.spline(times,1000*MEGmeantime7Hz[3,],df=20)
lines(spl7c$x,spl7c$y,col='blue',lwd=2)
spl7d <- smooth.spline(times,1000*MEGmeantime7Hz[4,],df=20)
lines(spl7d$x,spl7d$y,col='orange',lwd=2)

# lines(times,1000*MEGmeantime7HzASD[1,],lwd=2,col='red',lty=2)
# lines(times,1000*MEGmeantime7HzASD[2,],lwd=2,col='green',lty=2)
# lines(times,1000*MEGmeantime7HzASD[3,],lwd=2,col='blue',lty=2)
# lines(times,1000*MEGmeantime7HzASD[4,],lwd=2,col='orange',lty=2)
spl7aASD <- smooth.spline(times,1000*MEGmeantime7HzASD[1,],df=20)
lines(spl7aASD$x,spl7aASD$y,col='red',lwd=2,lty=2)
spl7bASD <- smooth.spline(times,1000*MEGmeantime7HzASD[2,],df=20)
lines(spl7bASD$x,spl7bASD$y,col='green',lwd=2,lty=2)
spl7cASD <- smooth.spline(times,1000*MEGmeantime7HzASD[3,],df=20)
lines(spl7cASD$x,spl7cASD$y,col='blue',lwd=2,lty=2)
spl7dASD <- smooth.spline(times,1000*MEGmeantime7HzASD[4,],df=20)
lines(spl7dASD$x,spl7dASD$y,col='orange',lwd=2,lty=2)

# lines(times,1000*MEGmeantime7HzCON[1,],lwd=2,col='red',lty=3)
# lines(times,1000*MEGmeantime7HzCON[2,],lwd=2,col='green',lty=3)
# lines(times,1000*MEGmeantime7HzCON[3,],lwd=2,col='blue',lty=3)
# lines(times,1000*MEGmeantime7HzCON[4,],lwd=2,col='orange',lty=3)
spl7aCON <- smooth.spline(times,1000*MEGmeantime7HzCON[1,],df=20)
lines(spl7aCON$x,spl7aCON$y,col='red',lwd=2,lty=3)
spl7bCON <- smooth.spline(times,1000*MEGmeantime7HzCON[2,],df=20)
lines(spl7bCON$x,spl7bCON$y,col='green',lwd=2,lty=3)
spl7cCON <- smooth.spline(times,1000*MEGmeantime7HzCON[3,],df=20)
lines(spl7cCON$x,spl7cCON$y,col='blue',lwd=2,lty=3)
spl7dCON <- smooth.spline(times,1000*MEGmeantime7HzCON[4,],df=20)
lines(spl7dCON$x,spl7dCON$y,col='orange',lwd=2,lty=3)

@@

lines(spl7bASD$x,spl7bASD$y/spl7cASD$y,col='blue',lwd=2,lty=2)
lines(spl7bASD$x,spl7bASD$y/spl7dASD$y,col='orange',lwd=2,lty=2)

lines(spl7bCON$x,spl7bCON$y/spl7cCON$y,col='blue',lwd=2,lty=3)
lines(spl7bCON$x,spl7bCON$y/spl7dCON$y,col='orange',lwd=2,lty=3)

>>>>

@@

lines(times,1000*MEGmeantime5Hz[1,],lwd=2,col='red')
lines(times,1000*MEGmeantime5Hz[2,],lwd=2,col='green')
lines(times,1000*MEGmeantime5Hz[3,],lwd=2,col='blue')
lines(times,1000*MEGmeantime5Hz[4,],lwd=2,col='orange')
spl5a <- smooth.spline(times,1000*MEGmeantime5Hz[1,],df=20)
lines(spl5a$x,spl5a$y,col='red',lwd=2)
spl5b <- smooth.spline(times,1000*MEGmeantime5Hz[2,],df=20)
lines(spl5b$x,spl5b$y,col='green',lwd=2)
spl5c <- smooth.spline(times,1000*MEGmeantime5Hz[3,],df=20)
lines(spl5c$x,spl5c$y,col='blue',lwd=2)
spl5d <- smooth.spline(times,1000*MEGmeantime5Hz[4,],df=20)
lines(spl5d$x,spl5d$y,col='orange',lwd=2)

@@

@@

lines(times,1000*MEGmeantime7Hz[1,],lwd=2,col='red')
lines(times,1000*MEGmeantime7Hz[2,],lwd=2,col='green')
lines(times,1000*MEGmeantime7Hz[3,],lwd=2,col='blue')
lines(times,1000*MEGmeantime7Hz[4,],lwd=2,col='orange')
spl7a <- smooth.spline(times,1000*MEGmeantime7Hz[1,],df=20)
lines(spl7a$x,spl7a$y,col='red',lwd=2)
spl7b <- smooth.spline(times,1000*MEGmeantime7Hz[2,],df=20)
lines(spl7b$x,spl7b$y,col='green',lwd=2)
spl7c <- smooth.spline(times,1000*MEGmeantime7Hz[3,],df=20)
lines(spl7c$x,spl7c$y,col='blue',lwd=2)
spl7d <- smooth.spline(times,1000*MEGmeantime7Hz[4,],df=20)
lines(spl7d$x,spl7d$y,col='orange',lwd=2)

@@
